---
title: "rword2vec"
author: "Mukul Chaware"
date: "9 March 2016"
output: pdf_document
---

R Interface to google's word2vec. <br />
The word2vec tool takes a text corpus as input and produces the word vectors as output. It first constructs a vocabulary from the training text data and then learns vector representation of words. 

###Examples
<br />
To download sample text data, click [here](http://mattmahoney.net/dc/text8.zip).

(Currently, Linux CPU only)<br/>
To install rword2vec package:

```{r eval=F}
library(devtools)
install_github("mukul13/rword2vec")
```
<br />
To list all functions supported by rword2vec:<br />

```{r}
library(rword2vec)
ls("package:rword2vec")
```
<br />
<b>Training word2vec model</b>
<br />
To train text data to get word vectors:<br />
```{r eval=F}
model=word2vec(train_file = "text8",output_file = "vec.bin",binary=1)
```
<br />
<b>Distance</b>
<br />
To get closest words:<br />
```{r eval=T}
### file_name must be binary
dist=distance(file_name = "vec.bin",search_word = "king",num = 10)
dist
```
<br />
```{r eval=T}
### file_name must be binary
dist=distance(file_name = "vec.bin",search_word = "princess",num = 10)
dist
```
<br />
```{r eval=T}
### file_name must be binary
dist=distance(file_name = "vec.bin",search_word = "terrible",num = 10)
dist
```
<br />
<b>Word analogy</b><br />
To get analogy or to observe strong regularities in the word vector space:<br />
```{r eval=T}
### file name must be binary
ana=word_analogy(file_name = "vec.bin",search_words = "king queen man",num = 10)
ana
```
<br />
```{r eval=T}
### file name must be binary
ana=word_analogy(file_name = "vec.bin",search_words = "paris france berlin",num = 10)
ana
```
<br />
<b>Training word2phrase model</b><br />
To convert words to phrases:<br />
```{r eval=F}
word2phrase(train_file = "text8",output_file = "vec.txt")

### use this new text file to give word vectors
model=word2vec(train_file = "vec.txt",output_file = "vec2.bin",binary=1)
```
<br />
<b>Word count</b>
<br />
To do word count:<br />
```{r eval=F}
### to count word occurences in input file
vocab_count(file_name="text8",vocab_file="vocab.txt",min_count = 20)
d=read.table("vocab.txt")
head(d)
```
```{r,eval=T,echo=F}
{
d=read.table("vocab.txt")
head(d)
}
```
<br />
<b>Getting model as text file</b><br />
To convert binary output file to text format:<br />
```{r eval=F}
###convert .bin to .txt
bin_to_txt("vec.bin","vector.txt")
```

### Resources
* [Github Repo](https://github.com/mukul13/rword2vec)
* [word2vec](https://code.google.com/archive/p/word2vec/) 
